Using cosmic variance to constrain the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1

### 2013-05-20 paper/ms.tex
starting the discussion section + new plots

\begin{figure}
\begin{center}
\includegraphics[width=0.95\linewidth,angle=0]{./plots/Fig2_match_P5.pdf}\\
\vspace{5mm}
\includegraphics[width=0.95\linewidth,angle=0]{./plots/Fig2_random_P5.pdf}\\
\vspace{5mm}
\includegraphics[width=0.95\linewidth,angle=0]{./plots/Fig2_full_P5.pdf}
\end{center} 
\caption{$M_{\rm min}$-$M_{\rm max}$ plane for all models with
  $P>0.05$ in the three different of grouping the mock fields. In the
  case of the {\tt match} and {\tt random} methods the  color code
  corresponds to the number of mock surveys that are found to
  be compatible with observations. For the {\tt full} method the
  colour code corresponds to the results of $100$ times the maximum $P$ value
  resulting from the KS test. \label{figure:landscape}.}  
\end{figure}

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig3_match_P5.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig3_random_P5.pdf}\\
\end{center} 
\caption{$M_{\rm min}$-$M_{\rm max}$ plane for all models with
  $P>0.05$\label{figure:f_escape}.} 
\end{figure*}

@@

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/match_large_correlation_selected_models.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/match_full_correlation_selected_models.pdf}
\end{center} f
\caption{ mean ACFs   and their correponding standard deviation (error
  bars)  of some selected models in different mass ranges over the 7
  subfields  f the SSA22 field (left) and the entire 12 field sample
  (rigth) using thematch
  configuration. \label{figure:correlation_match} }

@@

>>>>

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig2_match_P5.pdf}
\vspace{5mm}
\includegraphics[width=0.49\linewidth,angle=0]{./plots/Fig3_match_P5.pdf}\\
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig2_random_P5.pdf}
\hspace{5mm}
\includegraphics[width=0.49\linewidth,angle=0]{./plots/Fig3_random_P5.pdf}\\
\end{center} 
\caption{$M_{\rm min}$-$M_{\rm max}$ plane for all models with
  $P>0.05$ in the three different of grouping the mock fields. In the
  case of the {\tt match} and {\tt random} methods the  color code
  corresponds to the number of mock surveys that are found to
  be compatible with observations. For the {\tt full} method the
  colour code corresponds to the results of $100$ times the maximum $P$ value
  resulting from the KS test. \label{figure:landscape}.}  
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_match_mass_mock_and_f_occ.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_random_mass_mock_and_f_occ.pdf}
\end{center} 
\caption{Favored models when the constraints on the maximal number of
  consistent mocks and the observational constrain on the occupation
  fraction are included.
  \label{figure:mock_and_f_occ}}  
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/match_large_correlation_selected_models.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/match_full_correlation_selected_models.pdf}
\end{center} f
\caption{ mean ACFs   and their correponding standard deviation (error
  bars)  of some selected models in different mass ranges over the 7
  subfields  f the SSA22 field (left) and the entire 12 field sample
  (rigth) using thematch
  configuration. \label{figure:correlation_match} }  
  \end{figure*}

@@

When we include the tightest constraints on the mock catalogs, we find
that there are 30 set of parameters of our model, out of the original
90000 initial models, that are consistent with the observational
constraints at redshift $3.1$: the distribution of the number density,
the inferred values for the average occupation fraction and the
angular correlation function.

The final 30 models can be distributed into two families of the same
size. The first, where the range $M_{\rm min}-M_{\rm max}$ is narrow,
typically of less than $<1.0$ dex. While in the second familiy the
extent $>1.0$ dex. In the first case the minimum halo mass is found to
be in a wide range $10^{10}\hMsun <M_{\rm min}< 10^{11.5}\hMsun$ while
in the second case, only models with $M_{\rm min}\sim 10^{10.9}\hMsun$
are compatible with the observational contraints. In what follows we
discuss the implications of the existence of these two families of
models.
